---
title: "Day 1 Interactive Session 2"
author: "Wylie Hampson"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

### Logs and exponents in R

Some examples of using `log()` function and `exp()` function in R

```{r}
# Examples of logarithms

log(4)

# Examples of exponents

exp(5)

# A test of log()

log(exp(1))

```

### Creating sequences of values

```{r}
# A seqence from 1 to 20, by 1

ex_1 <- seq(from = 1, to = 20, by = 1)

ex_2 <- seq(from = 0, to = 40, by = 0.2)

ex_3 <- seq(from = 1, to = 5000, by = 10)
```

### Create a function for logistic growth

Given the carrying capacity, initial population, the growth rate, and time, use the logistic growth model to estimate the population at that time.

```{r}
pop_logistic <- function(capacity, init_pop, rate, time_yr) {
  
  capacity / (1 + ((capacity - init_pop) / init_pop) * exp(-rate * time_yr))
  
}


pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = 2.4)

```


### Try finding population over a sequence of times

```{r}
time_vec <- seq(from = 0, to = 50, by = 0.5)

```

Now let's estimate the population over that range of times, given capacity = 2580, initial population = 230, rate = 0.32

```{r}
chipmunk_pop <- pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = time_vec)

```

### Create a data frame and plot chipmunk population over time

```{r}

chipmunk_df <- data.frame(time_vec, chipmunk_pop)

```


### Create a bare minimum ggplot graph:

```{r}
ggplot(data = chipmunk_df, mapping = aes(x = time_vec, y = chipmunk_pop)) + 
  geom_point() + 
  labs(x = "Time (years)",
       y = "Chipmunk populations (individulas)",
       title = "Inyo NF chipmunks",
       subtitle = "Yay chipmunks!")
```












